Stability of Ensembles of Biological Networks

### 2014-09-11 journal.tex
compute cycle number and add to table
add plots with cycle number

The probability of \emph{a priori} stability and of stability to perturbations for all three component systems is given in Table \ref{tab:structstabmat3}. Fig. \ref{fig:stab3x3} shows the probability of stability to perturbations for all three component systems.

@@

% \begin{table}[h]
\begin{longtable}{ c || c | c | c }
\hline
matrix & connectivity & \specialcell{probability of stability\\to perturbation} & probability of stability\\
\hline
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 0\\
0 & 0 & 1\\
\end{pmatrix}$ & 3 & 0.499 & 0.126\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 4 & 0.505 & 0.121\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 4 & 0.622 & 0.127\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.595 & 0.121\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 5 & 0.494 & 0.128\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.41 & 0.061\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.43 & 0.078\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.605 & 0.12\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 0\\
\end{pmatrix}$ & 5 & 0.405 & 0.06\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 5 & 0.698 & 0.122\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 5 & 0.587 & 0.128\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 0\\
0 & 1 & 1\\
\end{pmatrix}$ & 5 & 0.707 & 0.127\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.578 & 0.121\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.487 & 0.081\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.543 & 0.098\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.501 & 0.088\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.662 & 0.123\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 6 & 0.467 & 0.079\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.583 & 0.13\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 6 & 0.659 & 0.124\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.751 & 0.124\\
$\begin{pmatrix}
1 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 0.604 & 0.097\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.564 & 0.103\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.475 & 0.068\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 0.591 & 0.108\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.717 & 0.119\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 0.648 & 0.122\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 0.627 & 0.105\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 0.577 & 0.093\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 0.639 & 0.109\\
$\begin{pmatrix}
1 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 9 & 0.638 & 0.106\\
\caption{{\bf Probability of stability under resampling and \emph{a priori} stability for three component systems estimated via Monte Carlo sampling.} All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat3}
\end{longtable}
%
% \end{table}

>>>>

The probability of \emph{a priori} stability and of stability to perturbations for all three component systems is given in Table \ref{tab:structstabmat3}. Fig. \ref{fig:connectcycle3D3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity and number of cycles. Fig. \ref{fig:stab3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity. Fig. \ref{fig:cycle3x3} shows the probability of stability to perturbations for all three component systems as a function of the number of simple cycles (elementary circuits) of length greater than one in the corresponding directed graph \cite{Johnson1975}.

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.8\columnwidth]{fig/connectcycle3D3x3.pdf}
\caption{{\bf Plot of stability to perturbations versus number of cycles and connectivity for three component systems.} }
\label{fig:connectcycle3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.8\columnwidth]{fig/cycle3x3.pdf}
\caption{{\bf Plot of stability to perturbations versus number of cycles for three component systems.} }
\label{fig:cycle3x3}
\end{figure}

\pagebreak

% \begin{table}[h]
\begin{longtable}{ c || c | c | c | c }
\hline
matrix & connectivity & cycle number & \specialcell{probability of stability\\to perturbation} & probability of stability\\
\hline
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 0\\
0 & 0 & 1\\
\end{pmatrix}$ & 3 & 0 & 0.496 & 0.122\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 4 & 1 & 0.496 & 0.13\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 4 & 0 & 0.626 & 0.128\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.602 & 0.127\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 5 & 2 & 0.496 & 0.122\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 2 & 0.405 & 0.061\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.429 & 0.081\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.597 & 0.129\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 0\\
\end{pmatrix}$ & 5 & 2 & 0.408 & 0.062\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 5 & 0 & 0.693 & 0.125\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.606 & 0.124\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 0\\
0 & 1 & 1\\
\end{pmatrix}$ & 5 & 0 & 0.705 & 0.131\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.578 & 0.115\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 3 & 0.489 & 0.085\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.548 & 0.091\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.493 & 0.087\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 1 & 0.669 & 0.128\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 6 & 3 & 0.474 & 0.086\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.587 & 0.12\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 6 & 1 & 0.656 & 0.121\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 6 & 0 & 0.741 & 0.125\\
$\begin{pmatrix}
1 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 1 & 0.596 & 0.098\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 3 & 0.572 & 0.094\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 5 & 0.465 & 0.075\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 3 & 0.592 & 0.105\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 7 & 1 & 0.713 & 0.122\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 2 & 0.642 & 0.125\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 2 & 0.628 & 0.11\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 5 & 0.578 & 0.092\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 3 & 0.647 & 0.115\\
$\begin{pmatrix}
1 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 9 & 5 & 0.635 & 0.11\\
\caption{{\bf Probability of stability under resampling and \emph{a priori} stability for three component systems estimated via Monte Carlo sampling.} All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat3}
\end{longtable}
%
% \end{table}
